
\poemtitle{beach blanket}
%\settowidth\versewidth{}
\begin{verse} %[\versewidth]
i awoke early this morning \\
and wrapped myself in the blanket \\
we sat on at the beach \\
after swimming in the ocean, \\
wrapped close as we watched the windy sunrise \\
cool and sandy under the stars as it \\
supported our embraces and kisses

i wrapped myself for warmth and comfort \\
and sat in the middle of the floor and \\
waited, as patiently as i could, for  \\
my fears and doubts to leave me, to  \\
dissolve or evaporate, to ebb from my shore

but nothing worked. not silence, nor \\
tears, nor prayers changed who \\
i was, or you are or what we have become. \\
i was left with the crushing thought \\
that love has found us despite ourselves.

if i open this door what else will  \\
walk through it? surely we have been \\
visited by joy, silliness and lust. \\
longing and confusion have also made an appearance. \\
but won't guilt come, and craving and \\
possession and won't one of us, at \\
some point, want the upper hand?

can either of us stand to rearrange  \\
these rooms again, to fit our stuff together \\
to lug our bags and boxes into one space \\
and push and pull and lift and sit \\
and cry and keep trying, never still

you stepped into some room in my heart \\
that i didn't know existed, had forgotten to \\
wall off or warn people away from. \\
i am glad you found it, but i am still \\
unreconciled to a presence in this space

so in the end i just fiddled with  \\
that old blanket. tied off some loose threads, \\
examined it for tears, stains, unraveled places. \\
and i found enough to make me realize that \\
after many years of use on beds and couches, \\
neglected in a closet, wrapped around the dog, \\
it was still whole, and would still cover us
\end{verse}
