\poemtitle{on painting my apartment}
\begin{verse}
this solitary occupation \\
slowing going over every inch of a wall that i merely glance past tomorrow \\
cleaning, checking, painting, checking, watching. \\
seeing all the little things that I never need look at again \\
all those little changes will be a featureless plane tomorrow, \\
paying attention to the invisible tomorrow. \\
all of the marks, mistakes, mishaps \\
all of the small things that leave these little marks in us \\
doors banged against walls \\
locks pushed in, frames cracked \\
hinges hanging slightly out of balance \\
small echos of what brought us here \\
(were you the scared one or the angry one  \\
when you pushed that door in? \\
no matter, aren’t they the same thing?) \\
transmitting our pain to some else.  \\
those rare moments when we believe we are not alone.

when you go to these great rooms they always say \\
``if these walls could talk...'' \\
if you could be still enough to listen \\
i think you will find that they do \\
but they don’t hold those temporary disturbances of the air \\
they hold the deep marks, the stuff that won’t rub off. \\
when i go to the oval office i don’t want to see where they sat \\
and made the great proclamation that saved us all \\
from the latest and gravest threat we entrusted them with. \\
i want to search for that hand print Lincoln left on the wall \\
where he steadied himself after reading the first reports \\
from Antietam or Cold Harbor, comprehending his destiny. \\
all of those things they can’t carve into the memorial
\end{verse}
