\poemtitle{prophets}
\begin{verse}
i reflect on the fact that this must \\
be one of the most dangerous jobs out \\
there. no wonder Johna ran like hell \\
when you gave him his orders. \\
how can anyone face that dread task \\
of explaining again and over again  \\
what you expect from us. it seems \\
simple enough, but through all the \\
repetition, variation, theatrics \\
and simple words we reject it, \\
and more often then not we kill  \\
the messenger to show you what \\
we think of this constant nagging.

but then my thoughts turn away \\
from what we've done, do, are \\
most likely are preparing to do \\
again any moment, and back to you. \\
what do you think when they return \\
to you? dumped in the garden in the \\
middle of night. bound hands, bullet holes, \\
signs of torture and human frailty. \\
frail old men and strong young men alike. \\
some fancy caskets, but usually just a body, \\
beaten, naked and alone. do you think \\
it was unfair to burden them with your \\
words? how could you assign this task? \\
are you angry? disappointed, resigned? \\
how do you find the courage to try again? \\
select another one with a new message \\
(that is always the same message) \\
and deliver that sweet child to  \\
an almost certain death at the hands \\
of the people who most needed to hear \\
what you had to say. maybe you feel it \\
is your duty, or maybe you are resolved \\
to fulfill some kind of mad quota, like \\
public service announcements interrupting \\
this show of force, violence and lust we \\
find ourselves addicted to.

i know your love and imagination transcends  \\
this meager world we inhabit and all that \\
is incomprehensible to me is simple logic \\
to you, and i suppose that is the problem \\
if you think about it, but how can you  \\
continue, in the face of all we have done? \\
how can you still love us? how can love find space \\
in this brutal monument we have constructed in your honor?
\end{verse}
