
\poemtitle{bat-zabbal}\footnote{latin: Julia Aurelia Zenobia}
\begin{verse}
i stumbled into the gallery thinking about where i should meet you \\
i would offer you a riddle, a time and the name of a painting \\
and see if you would bite, solve the puzzle, come to me, try a bit \\
to see if you were willing to extend yourself a litte, reach, \\
ask the guard where the painting was, find out that the sullen,
disinterested guards know every painting, each master, will offer \\
an opinon on the heritage of each piece and can lead you to Tiepolo \\
down in the back gallery, at the end of the hall. \\
Queen Zenobia stands in her armor, facing future \\
rallying once more the exhausted, rapt soldiers. \\
tired of battle, but ready to follow her into this last one.

and I'd be waiting for you on the couch, hoping you would see yourself \\
in that warrior, conquering Egypt and Anatolia, defeating the status quo 

but i can't imagine you would see that. just a quizzical look at \\
one more odd thing i've done to impress you, wondering why i could \\
be so sweet and so strange in one moment and why i continued to talk \\
past you when all you wanted was someone to lead you on. 

maybe we should meet in front of el greco's madonna \\
that forlorn look at that pacific child. yearning sweetness \\
for something that was not quite yours but held so close. 

i think all warriors look back at the battles behind them \\
and see the waste, the loss, enemies and comrades broken alike, \\
and wonder how desolation can be called victory. \\
most victors can at least speak victory, even if \\
they can't really feel it any more, but you look back and \\
only see failure, carnage, destruction and loss.

but the victories remain, and your conquest is beyond \\
the faintest hope of most of us. you have conquered \\
and emerged a hero of your own life. open, sweet and \\
loving after so much struggle, setback and loneliness. \\
that gray raiment you see in the mirror is not a dingy \\
white dress but the well-worn armor only the brave posses

i am puzzled, confused, perplexed, unnerved, unsure of whether to \\
treat you as the great warrior you are, or see the madonna in you, \\
the sweet sad object of someone else's story, or to see the battle \\
tested heart, strong, resilient, doubtful. \\
victorious on the field, but unprepared for the battle within.
\end{verse}
