
\poemtitle{reunion}
\settowidth\versewidth{he still couldn't open his heart to you, to expose that steadfast wanting }
\begin{verse}[\versewidth]
what was going through your mind as he approached, \\
bowing, almost abject, as you ran to greet  him? \\
what had torn you apart? was it forgotten, forgiven, overlooked? \\
had you settled the score in your own heart? \\
or was it a gift to the past, that old lover we can't quite forget? 

did you father’'s blessing really not matter to you,  \\
squandered like they said? \\
that's the story we have today, but there must be more to it. \\
here he was, welcome with an open heart \\
the glad heart of a settled man, anchored in his land \\
"I have plenty my brother, keep what belongs to you"\footnote{Gen 33:9}

here he was before you again, changed too, grown is his way \\
but still wary, posturing, trying to position himself for what's next \\
his vulnerable uprooted house pushed to the front as a shield. \\
reaching out to his next blessing, stubborn fingers grasping the future. \\
he still couldn't open his heart to you, to expose that steadfast wanting.

was he always worried, unsure, calculating even? \\
struggling all night to appease heaven and earth,  \\
conjuring blessings from the future of that hard land. \\
(did you think to ask him why he was limping?) \\
each of you with plenty but seeing a different future 

i can't let this go, this choice, this unfinished room. \\
why couldn't it be different, together, reconciled, whole \\
that same red stain handed down the generations, \\
while he didn't even have the courage to face you. \\
what were you doing when you realized he chose the other road? 

\end{verse}
