
\begin{verse}
the fruit of knowledge is the root of the fall \\
but i don't recall exactly what that knowledge was.\\
of good and evil, of the knowledge that God had. \\
but what did we learn of it? i doubt the garden was \\
without pain or loss. it was after all a garden,  \\
life cycling around in a frenetic dance of birth,  \\
growth, ripening, death, destruction and around again.

what did we understand then that we didn't know before? \\
perhaps we understood that God knew the nature of good \\
and evil but could do nothing about it. perhaps we understood \\
that God was as poor and helpless within this great turning \\
as we were. perhaps we understood that God clung to us \\
in the same way we would soon cling to God.

and how did we all decide to part ways and go out \\
to till fields and give birth and willingly set in motion  \\
our own wheels of birth, growth, ripening and destruction \\
that were ours alone, the stories we would write  \\
to justify all we had done? \\
was it too embarrassing, humiliating, intimate, for God \\
to know we knew, to accept our pity, to look us in the eye? \\
or did we think that we could do this on our own? knowing \\
that there was no secret behind it, just constant trying \\
with the knowledge that you could never quite succeed.  \\
our maybe we both thought that we should live apart \\
bury our secret and look forward to the day when we \\
could come together and embrace, secure in the knowledge \\
that we need each other to walk this path with our eyes open.
\end{verse}
